A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2021-02-14 04_MetaAnalysis.Rmd
Add footnotes and correct row labels

# create data.frame
results_mv <- data.frame(
   moderator = c(
   "Intercept / No Spray control",
   "Early",
   "Recommended",
   "Recommended+",
   "Late",
   "Late+"
   ),
   N = PM_mv$g.levels.k,
   k = k5,
   Effect = round(PM_mv$b, 4),
   se = round(PM_mv$se, 4),
   CI_lower = round(PM_mv$ci.lb, 4),
   CI_upper = round(PM_mv$ci.ub, 4),
   z_val = round(PM_mv$zval, 4),
   p_val = reportP(PM_mv$pval, AsNumeric = FALSE, P_prefix = FALSE)
)

@@

yield_estimates_table <- 
   flextable(results_mv[c(2:6), c(1,3:8,10)]) %>%
   align(j = 3:8, align = "center", part = "all") %>%
   fontsize(size = 8, part = "body") %>%
   fontsize(size = 10, part = "header") %>%
   italic(italic = TRUE, part = "header") %>%
   set_caption("Table 2: Estimated mungbean yield mean difference to the no spray control (intercept) for each spray schedule treatment. Estimates were calculated from a network meta-analysis of data obtained from grey literature reports of 'k' field trials undertaken in Eastern Australia. P values indicate statistical significance in comparison to the intercept.") %>%
   autofit()

>>>>

# create data.frame
results_mv <- data.frame(
   Moderator = c(
   "Intercept / No Spray control",
   "Early",
   "Late",
   "Late+",
   "Recommended",
   "Recommended+",
   ),
   N = PM_mv$g.levels.k,
   k = k5,
   Effect = round(PM_mv$b, 4),
   se = round(PM_mv$se, 4),
   CI_lower = round(PM_mv$ci.lb, 4),
   CI_upper = round(PM_mv$ci.ub, 4),
   z_val = round(PM_mv$zval, 4),
   p_val = reportP(PM_mv$pval, AsNumeric = FALSE, P_prefix = FALSE)
)

@@

yield_estimates_table <- 
   flextable(results_mv[c(2,5,6,3,4), c(1,3:8,10)]) %>%
   align(j = 3:8, align = "center", part = "all") %>%
   fontsize(size = 8, part = "body") %>%
   fontsize(size = 10, part = "header") %>%
   italic(italic = TRUE, part = "header") %>%
   set_caption("Table 2: Estimated mungbean yield mean difference to the no spray control (intercept) for each spray schedule treatment. Yield estimates (u) were calculated from a network meta-analysis of data obtained from grey literature reports of 'k' field trials undertaken in Eastern Australia. P values indicate statistical significance in comparison to the intercept.") %>%
   autofit() %>%
   footnote(i = 1,
            j = c(2:4,6:8),
            value = as_paragraph(c(
               "number of treatment means categorised to each spray schedule",
               "number of trials with the respective spray schedule",
               "estimated mean yield determined by the meta-analysis",
               "Lower range of the 95% confidence interval",
               "Upper range of the 95% confidence interval",
               "indicates the significance between each respective spray schedule and the no spray control (intercept)"
                                   )),
            ref_symbols = letters[1:6],
            part = "header", inline = TRUE
            )

### 2021-02-14 05_severity_metaAnalysis.Rmd
Add footnotes and correct row labels

# create data.frame
results_mv <- data.frame(
   moderator = c(
   "Intercept / No Spray control",
   "Early",
   "Recommended",
   "Recommended+",
   "Late",
   "Late+"
   ),
   N = PMsev_mv$g.levels.k,
   k = k5,
   Effect = round(PMsev_mv$b, 4),
   se = round(PMsev_mv$se, 4),
   CI_lower = round(PMsev_mv$ci.lb, 4),
   CI_upper = round(PMsev_mv$ci.ub, 4),
   z_val = round(PMsev_mv$zval, 4),
   p_val = reportP(PMsev_mv$pval, AsNumeric = FALSE, P_prefix = FALSE)
)

@@

disease_estimates_table <- 
   flextable(results_mv[c(2:6), c(1,3:8,10)]) %>%
   align(j = 3:8, align = "center", part = "all") %>%
   fontsize(size = 8, part = "body") %>%
   fontsize(size = 10, part = "header") %>%
   italic(italic = TRUE, part = "header") %>%
   set_caption("Table 3: Estimated powdery mildew severity mean difference ($u$) to the no spray control (intercept) for each spray schedule treatment. Estimates were calculated from a network meta-analysis of data obtained from grey literature reports of (k) field trials undertaken in Eastern Australia. P values indicate statistical significance in comparison to the intercept.") %>%
   autofit()

>>>>

# create data.frame
results_mv <- data.frame(
   Moderator = c(
   "Intercept / No Spray control",
   "Early",
   "Late",
   "Late+",
   "Recommended",
   "Recommended+"
   ),
   N = PMsev_mv$g.levels.k,
   k = k5,
   Effect = round(PMsev_mv$b, 4),
   se = round(PMsev_mv$se, 4),
   CI_lower = round(PMsev_mv$ci.lb, 4),
   CI_upper = round(PMsev_mv$ci.ub, 4),
   z_val = round(PMsev_mv$zval, 4),
   p_val = reportP(PMsev_mv$pval, AsNumeric = FALSE, P_prefix = FALSE)
)

@@

disease_estimates_table <-
   flextable(results_mv[c(2,5,6,3,4), c(1, 3:8, 10)]) %>%
   align(j = 3:8, align = "center", part = "all") %>%
   fontsize(size = 8, part = "body") %>%
   fontsize(size = 10, part = "header") %>%
   italic(italic = TRUE, part = "header") %>%
   set_caption(
      "Table 3: Estimated powdery mildew severity mean difference ($u$) to the no spray control (intercept) for each spray schedule treatment. Estimates were calculated from a network meta-analysis of data obtained from grey literature reports of (k) field trials undertaken in Eastern Australia. P values indicate statistical significance in comparison to the intercept."
   ) %>%
   autofit() %>%
   footnote(
      i = 1,
      j = c(2:4, 6:8),
      value = as_paragraph(
         c(
            "number of treatment means categorised to each spray schedule",
            "number of trials with the respective spray schedule",
            "estimated mean yield determined by the meta-analysis",
            "Lower range of the 95% confidence interval",
            "Upper range of the 95% confidence interval",
            "indicates the significance between each respective spray schedule and the no spray control (intercept)"
         )
      ),
      ref_symbols = letters[1:6],
      part = "header",
      inline = TRUE
   )
